Merits of hypermedia systems

### 2013-06-07 dagstuhl-2013/position.tex
spell check
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@588 43ef1190-90fd-4dd7-a769-d0121f02b80e

My primary research interest is the optimization of SPARQL queries in
a federated regime, as we have noted that this is not practical
because the federation engine has insufficient information to
optimize, or the information is so large that it defeats the purpose
of optimizations to begin with. I plan to help remedy this problem by
computing very compact digests and expose them in the service
description. I have not yet published any articles on this topic, but
the research is in the immediate extension of
SPLENDID\cite{splendid}. My secondary research interest is replacing
the practice of benchmarking by using statistical design of
experiment.

@@

To bring forward a concrete example of how to make a serialized RDF
graph into a hypermedia type, we suggest adding some triples to every
resource (where prefixes are omitted for brevity):

@@

For example a pizza baker publishes Linked Data about pizzas they
sell, including data sufficient to create a sophisticated search and
sales application. The Linked Data will then include triples that
state explicitly how the order should be placed, i.e. what resources
need updating. Moreover, the may not only want to sell pizzas, but
also drinks. Thus, the Linked Data presented to the application should
not only be a Symetric Concise Bounded Description, as common today,
but careful designed to provide exactly the data needed to optimize
sales.

>>>>

My primary research interest is the optimisation of SPARQL queries in
a federated regime, as we have noted that this is not practical
because the federation engine has insufficient information to
optimise, or the information is so large that it defeats the purpose
of optimisations to begin with. I plan to help remedy this problem by
computing very compact digests and expose them in the service
description. I have not yet published any articles on this topic, but
the research is in the immediate extension of
SPLENDID\cite{splendid}. My secondary research interest is replacing
the practice of benchmarking by using statistical design of
experiment.

@@

To bring forward a concrete example of how to make a serialised RDF
graph into a hypermedia type, we suggest adding some triples to every
resource (where prefixes are omitted for brevity):

@@

For example a pizza baker publishes Linked Data about pizzas they
sell, including data sufficient to create a sophisticated search and
sales application. The Linked Data will then include triples that
state explicitly how the order should be placed, i.e. what resources
need updating. Moreover, the may not only want to sell pizzas, but
also drinks. Thus, the Linked Data presented to the application should
not only be a Symmetric Concise Bounded Description, as common today,
but careful designed to provide exactly the data needed to optimise
sales.
